A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-12-06 paper_review/response_1.txt

REVIEWER COMMENT
----------
Line 604-608: The statement that the density from the transit
duration is inconsistent with that expected for the M dwarf "B" cites
Table 2 and Choi+2016, but that Table does not appear to provide any
information on "B", and the Choi+2016 reference is just for the Mesa
models. A density of 2 g/cm3 (or lower) is possible for an M dwarf on
the pre-main sequence, depending on the mass, age and model used.

RESPONSE
----------

> Thank you for catching this -- this citation is indeed deprecated
> and erroneously was not updated during the writing process.  The
> final adopted calculation was based on the stellar masses and radii
> from the Baraffe+2015 models, rather than the MESA models
> (Choi+2016).  These models are available from
> http://perso.ens-lyon.fr/isabelle.baraffe/BHAC15dir/.  We used
> their 2MASS synthetic photometry to estimate the companion's mass,
> as follows.
>
>     m_K = 11.194 (2MASS)
>     m_K,A = 11.31
>     m_K,B = 13.68 (NIRC2)
>     m-M = 5*log10(329.5) - 5 = 7.59
>     -> M_K,A = 3.72
>     -> M_K,B = 6.09
>
> Assuming an age of 40 Myr, this yields M_comp = 0.31 Msun, by
> interpolating between the Baraffe 0.3 and 0.4 Msun values (M_K =
> 6.12 and 5.71, respectively).  Assuming an age of 30 Myr yields
> M_comp = 0.27 Msun (M_K=6.48, and 5.90 for 0.20 and 0.30 Msun).
> The bilinear interpolation at 38 Myr (our nominal age) yields
> M_comp=0.30 Msun, Teff=3408K, R=0.451 Rsun, and log(g)=4.60.
> In our original manuscript, we quoted a companion mass of 0.33
> Msun; this has been corrected in the revision.
>
> Given our age uncertainies (38 +/- 6 Myr), a plausible mass range
> based on these models for the companion is roughly 0.27 Msun to
> 0.33 Msun.  The model densities over the relevant ages and masses
> are
>
> 	age    mass        radius      density
>   32 Myr 0.300 Msun, 0.481 Rsun, 3.80 g / cm3
>   40 Myr 0.300 Msun, 0.443 Rsun, 4.86 g / cm3
>   32 Myr 0.330 Msun, 0.506 Rsun, 3.60 g / cm3
>   40 Myr 0.330 Msun, 0.467 Rsun, 4.58 g / cm3
>   32 Myr 0.350 Msun, 0.518 Rsun, 3.55 g / cm3
>   40 Myr 0.350 Msun, 0.479 Rsun, 4.50 g / cm3
>   38 Myr 0.300 Msun, 0.451 Rsun, 4.61 g / cm3
> 
> This means that for the argument concerning the stellar density
> inferred from the transit, the worst-case scenario would be that of
> a) the companion being more massive than expected  (~0.35 Msun),
> simultaneously with b) the system being younger than expected (~32
> Myr).  In this scenario, the companion star's density would be ~=
> 3.5 g/cc.  We've updated the text to reflect this uncertainty.

@@

REVIEWER COMMENT
----------
line 678-683: The Ca II HK activity indicator "S" as well as the
H-alpha equivalent width could be obtained from the HIRES spectrum.
Have the authors checked fora X-ray or UV (Galex) detection of this
star? The star is likely not detected but its worth a look. In the
same vein, the authors may wish to comment on whether the star's
infrared emission indicates or rule out a substantial debris disk --
the star is detected in WISE (and perhaps Spitzer?)

RESPONSE
----------

(NOTE: TODO: THIS RESPONSE STILL MIGHT BE UPDATED WITH A POSSIBLE
DEEPER ANALYSIS OF THE UV)

> Regarding the S-values, they are shown in the second panel of
> Figure 7, and are also reported in Table 6.  The line profile
> changes shown in Figure 12 suggested that the majority of the RV
> variation observed was due to starspot-induced variations.
> Quantitative measurements of the H-alpha EWs are not expected to
> change this picture, and so we opt to not include them.
>
> Regarding the NIR, UV, and X-ray detections, we searched Vizier
> within a radius of 4 arcseconds.
>
> For the X-ray (i.e., ROSAT), there were no reported detections in
> Vizier.
>
> For the NIR and the possibility of a debris disk, Kepler-1627 is
> detected in W1, W2, W3, and W4 (see
> kepler1627_vizier_photometry.png attached).  While W4 might be in
> excess of the usual Rayleigh-Jeans tail, and this could be
> quantified by fitting synthetic stellar atmospheres, this type of
> analysis is best done at the population level, particularly given
> the calibration uncertainties that are present in W4 (e.g., Cotten
> & Song 2016, ApJS 225 15).  Since Kepler-1627 has not been
> identified as even a candidate debris disk host in the previous
> literature that performs these population-level infrared excess
> analyses, we opt to not speculate on this topic.
>
> For the UV, Olmedo+2015 reported a coincident source with NUVmag of
> 19.052 +/- 0.017 [AB mags], with a NUV S/N of 65 (2015, ApJ, 813,
> 100), through the GALEX-CAUSE Kepler survey.  UV detections can
> sometimes be used as a youth indicator (e.g., Figure 9 of
> Newton+2021 AJ 161 65, which Newton et al attribute from the idea
> in Shkolnik+2011, ApJ 727 6).  For Kepler-1627, we have 2MASS J =
> 11.690+/-0.021, and therefore m_NUV-m_J = 7.36.  Given the Gaia
> (BP-RP)0 of 0.977, comparing to Figure 9 of Newton+2021 we find
> that Kepler-1627 overlaps with late-G type stars in Psc-Eri, the
> Pleiades, and the Hyades.  In other words, the UV flux is not a
> particularly strong diagnostic of the age for Kepler-1627 as an
> individual star.  
>
> To substantiate the latter claim, we cross-matched our lists of
> Pleaides and δ Lyr cluster members against 2MASS and GALEX.  The
> results are in galex_jmk.png and galex_bpmrp.png, attached.  We
> attempted including IC2602 as well, but only got a few matches
> because it was not observed.  We see that the earliest A and F
> stars in the del Lyr cluster (38 Myr) are brighter in the UV than
> the Pleiades sequence (112 Myr).  However, there's not really any
> information in this statement independent of the work that's
> already done in the paper using Gaia isochrones and the stellar
> rotation.

### 2021-12-06 paper/ms.tex
update response

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in \replaced{mini-Neptune}{Neptune-sized
planet} Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown \added{to clarify the direction along which
    parallax uncertainties are expected to produce erroneous
    clusters}.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f4a.pdf}
			\includegraphics[width=0.48\textwidth]{f4b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
		from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2.5V
		companion at $\rho \approx 0\farcs16$, which corresponds to a
		projected separation of $53\pm4$\,AU.  The inset shows a cutout of
		the stacked NIRC2 image (North is up, East is left, scale is set
		by the separation of the binary).  The lines show 5-$\sigma$
		contrast limits for the `Alopeke filters, and 6-$\sigma$ contrast
		limits for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia EDR3
		renormalized unit weight error (RUWE) point estimates for
		candidate $\delta$\,Lyr cluster members.  Since other members of
		the cluster with similar brightnesses have comparable degrees of
		photometric variability, the high RUWE independently suggests that
		Kepler\,1627 is a binary. 
		\label{fig:kep1627binary}
	}
\end{figure*}

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large \replaced{renormalized
unit weight error (RUWE),}{RUWE} relative to other members of the \cn\
\added{(RUWE$\approx$2.9; roughly the $98^{\rm th}$ percentile of the cluster's
distribution)}.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf \replaced{Possible}{Weak} evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities \replaced{are weakly}{might
    be} anti-correlated
    ($\approx$2-$\sigma$), which
    \replaced{might}{could} be caused by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The $\chi^2$ of the
best-fit line is $306.1$, with $n=140$ data points.  An alternative
model of a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion (BIC) between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive evidence
at best, particularly given the excess scatter in the transit timing
measurement uncertainties.}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:groundobs}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}
\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ \citep{baraffe_new_2015}.
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

@@

%\clearpage
\acknowledgements
\raggedbottom

>>>>

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in \replaced{mini-Neptune}{Neptune-sized
planet} Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported \replaced{M2.5}{M3}V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown \added{to clarify the direction along which
    parallax uncertainties are expected to produce erroneous
    clusters}.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f4a.pdf}
			\includegraphics[width=0.48\textwidth]{f4b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
		from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$\replaced{M2.5}{M3}V
		companion at $\rho \approx 0\farcs16$, which corresponds to a
		projected separation of $53\pm4$\,AU.  The inset shows a cutout of
		the stacked NIRC2 image (North is up, East is left, scale is set
		by the separation of the binary).  The lines show 5-$\sigma$
		contrast limits for the `Alopeke filters, and 6-$\sigma$ contrast
		limits for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia EDR3
		renormalized unit weight error (RUWE) point estimates for
		candidate $\delta$\,Lyr cluster members.  Since other members of
		the cluster with similar brightnesses have comparable degrees of
		photometric variability, the high RUWE independently suggests that
		Kepler\,1627 is a binary. 
		\label{fig:kep1627binary}
	}
\end{figure*}

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large \replaced{renormalized
unit weight error (RUWE),}{RUWE} relative to other members of the \cn\
\added{(RUWE$\approx$2.9; roughly the $98^{\rm th}$ percentile of the cluster's
distribution)}.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of \replaced{$M_{\rm B} \approx
0.33 M_{\odot}$}{$M_{\rm B} \approx 0.30 M_{\odot}$} and companion
temperature of \replaced{$T_{\rm eff,B} \approx 3450$}{$T_{\rm eff,B}
\approx 3408$} K.  The corresponding spectral type is roughly \replaced{M2.5}{M3}V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf \replaced{Possible}{Weak} evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities \replaced{are weakly}{might
    be} anti-correlated
    ($\approx$2-$\sigma$), which
    \replaced{might}{could} be caused by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The
best-fit line yields $\chi^2 = 306.1$, with $n=140$ data points.  An alternative
model of just a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive evidence
at best, particularly given the excess scatter in the transit timing
measurement uncertainties.}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:groundobs}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B \added{given its
nominal age of 38\,Myr and mass of 0.30\,$M_\odot$} is $\approx 4.6\,{\rm
g\,cm}^{-3}$ \citep{baraffe_new_2015}.
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.\added{ Adversarially assuming a younger age (32\,Myr) and a larger companion
mass (0.35\,$M_\odot$), the companion's density could be as low as $\approx 3.5\,{\rm
g\,cm}^{-3}$.  This is still in tension with the data.} While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

\clearpage
\acknowledgements
\raggedbottom
